---
title: "plot_10x_clk856_th"
author: "Dylan Ma"
date: "10/27/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# laod libs, setup
```{r}
library( tidyverse )
library( gtools )
library( magrittr )
library( ggrepel )
library( cowplot )
library( patchwork )
library( Seurat )
library( ComplexHeatmap )
library( circlize )
library( ggExtra )
library( ggpubr )
library( rvest )
library( viridis )
library( extrafont )
library( ggnewscale )
library( ggrepel )
library( corrplot )
library( qgraph )


# font_import()
# fonts()

setwd("~/Documents/GitHub/10X_Clk856_TH/")
options(stringsAsFactors = FALSE)

"%ni%" <- Negate("%in%")



theme_set( theme_cowplot() )

set.seed(123)

source("~/Documents/GitHub/10X_Clk856_TH/R/main_functions.R",local = knitr::knit_global())

```

# Gene list

```{r}

l.tfs <- read.csv("data/transcription_factors_in_flies.csv", row.names = 1) %>% 
  pull( x )

l.gpcr.ms <- scan("~/Documents/scRNA_seq/resource/list_GPCRs_matthias.csv", what=as.character())

l.npp <- scan("~/Documents/scRNA_seq/resource/neuropeptides_55.txt",what = character())

# ion channels:

l.ics <- read.csv("resource/ion_channels_flybase_gene_group.txt", sep = "\t") %>% 
  pull(SYMBOL) %>% unique()

# CAMs, get the table from FlyXCDB

url <-  "http://prodata.swmed.edu/FlyXCDB/info.list.new21_26.html"

l.cams <- url %>% 
  read_html() %>% 
  html_nodes("table") %>% 
  html_table(fill = T) %>% 
  as.data.frame() %>% 
  mutate( XC = as.character( XC)) %>% 
  filter( grepl("Ig|EGF|LRR|fn3|Cadherin", XC, ignore.case = T)) %>% 
  pull( Name ) %>% unique()

# chemical synaptic transmission

l.cstrans <- read.csv("resource/chemical_synaptic_transmission_GO_0007268_flybase.txt", sep = "\t") %>% 
  pull( SYMBOL ) %>% unique()

# ribosomal proteins

l.riboso <- read.csv("resource/ribosomal_proteins_flybase_gene_group.txt", sep = "\t") %>% 
  pull( SYMBOL ) %>% unique()

# RBP should exclude TFs, ribosomal proteins, microRNA and tRNAs

l.RBP <- read.csv("resource/RNA_bingding_protein_GO_0003723_flybase.txt", sep = "\t") %>% 
  filter( SYMBOL %ni% c(l.tfs, l.riboso) ) %>% 
  filter( !grepl("tRNA", SYMBOL, ignore.case =  TRUE)) %>% 
  filter( !grepl(":|mir", SYMBOL, ignore.case =  TRUE)) %>% 
  pull( SYMBOL ) %>% unique()


l.cams <- l.cams[l.cams%ni% c(l.gpcr.ms,l.npp)]
l.cstrans <- l.cstrans[l.cstrans %ni% c(l.tfs, l.gpcr.ms, l.cams,l.npp, l.RBP)]
l.ics <- l.ics[l.ics %ni% c(l.cams, l.cstrans)]

```

# seurat object

```{r}
s.raw <- readRDS("data/prepare_data_co-clustering_2021-11-01.rds")
s.raw.clustered <- readRDS("data/coclustering_celseq2_10x_seed_123_2021-11-01.rds")

s.all.subset <- readRDS("~/Documents/GitHub/10X_Clk856_TH/data/subset_confident_clock_th_clusters_removed_bad_cells_renamed_clusters_2021-11-01.rds")

s.all.subset$renamed_idents <- as.character(s.all.subset$renamed_idents )
s.all.subset$renamed_idents[s.all.subset$renamed_idents == "2"] = "2:Clk"
s.all.subset$renamed_idents[s.all.subset$renamed_idents == 25] <- "25:DN1p(4)"

DimPlot(s.all.subset, label = T) + 
  theme_minimal() +
  NoLegend()

```


# tsne and detected genes in raw seurat object

```{r}

pdf(save_pdf("tsne_raw_clustering_result"),width = 7.5)
DimPlot(s.raw.clustered, label = F)+
  NoLegend()
dev.off()


pdf(save_pdf("cell_percentage_in_raw_clustering"),width = 18, height = 8.5)
s.raw.clustered@meta.data %>% 
  dplyr::count(seurat_clusters,method) %>% 
  pivot_wider(names_from = method,values_from = n) %>% 
  mutate(percentage = ten_x / (ten_x+Celseq2)) %>% 
  pivot_longer(cols = Celseq2:ten_x, names_to = "method", values_to = "n") %>% 
  ggplot(aes(reorder( seurat_clusters, percentage), n, fill = method))+
  geom_col(position = "fill")+
  theme_cowplot()+
  scale_fill_brewer(palette = "Set2")+
  scale_y_continuous(labels = scales::percent_format())+
  labs(x="Clusters", y="Percentage")
dev.off()


pdf(save_pdf("number_of_detected_genes_raw_clustering"),width = 18,height = 8.5)

s.raw.clustered@meta.data %>% 
  select( seurat_clusters, nFeature_RNA, nCount_RNA) %>% 
  mutate( seurat_clusters = factor( seurat_clusters, levels = mixedsort(unique(as.character(seurat_clusters))))) %>% 
  ggplot(aes(seurat_clusters, nFeature_RNA, fill = seurat_clusters))+
  geom_boxplot(outlier.alpha = 0.0001) +
  ylim(0,5000)+
  theme_cowplot()+
  theme( legend.position = "none", axis.text.x = element_text(angle = 90))+
  labs(x="", y="Number of detected genes")
dev.off()

```


# plot top5 marker genes of all the clusters(filtered clusters)

```{r}

df.m <- read.csv("~/Desktop/phoebe/10x_clk856_TH/analysis/rds_data_clustering/DGE_negbinom_2021-11-24.csv",row.names = 1,stringsAsFactors = FALSE)

## compute mean per cluster
m.c.mean <- sapply( mixedsort( levels( s.all.subset@active.ident ) ), function( cluster ){ apply( exp( s.all.subset$RNA@data[ , s.all.subset@active.ident == cluster ] ) -1, 1, mean );  } );

df.m$TP10K.mean <- NA;
for ( ir in 1:nrow( df.m ) ){
    df.m$TP10K.mean[ ir ] <- m.c.mean[ as.character( df.m$gene[ ir ] ), as.character( df.m$cluster[ ir ] ) ];
}

df.m <- df.m[ , c( "gene", "cluster", "p_val_adj", "p_val", "avg_logFC", "pct.1", "pct.2", "TP10K.mean" ) ];

df.m.o <- df.m[ order( df.m$cluster, -df.m$avg_logFC ), ];
for ( gene in  unique( df.m.o$gene ) ){
    v.keep <- df.m.o$gene != gene | df.m.o$avg_logFC == max( df.m.o$avg_logFC[ df.m.o$gene == gene ] );
    df.m.o <- df.m.o[ v.keep, ];
}


df.tmp <- df.m.o[ df.m.o$p_val_adj < 0.01 & df.m.o$avg_logFC > log(1.5), ] %>% 
  mutate(cluster = factor( cluster, levels = mixedsort(unique(as.character(cluster)))))


tmp <- sapply( mixedsort( unique( df.m.o$cluster ) ), function(x){ v <- df.m.o$gene[ df.m.o$cluster == x ]; v <- v[ 1:min(5,length(v) )]; return(v); } )
str( tmp );

v.features <- as.vector( tmp ) %>% unlist()

s.all.subset <- ScaleData(object = s.all.subset,assay = "RNA",features = rownames(s.all.subset@assays$RNA@data))


s.all.subset@meta.data$renamed_idents <- s.all.subset@active.ident
s.all.subset@meta.data$renamed_idents <- factor( s.all.subset@meta.data$renamed_idents, levels = mixedsort(unique(as.character(s.all.subset@meta.data$renamed_idents))))
s.all.subset@active.ident  <- s.all.subset@meta.data$renamed_idents

pdf(save_pdf("top5_marker_genes_all_filtered_clusters"),width=22, height=18)
p <- DoHeatmap( s.all.subset, assay="RNA", features=v.features, slot='scale.data', size=4.0, label=FALSE) + 
  scale_fill_gradientn(colors = c("blue", "white", "red") ) + 
  scale_fill_viridis()+
  ggtitle( "Top5 marker genes" )
print( p );dev.off()

```

# tsne plot without lables
```{r}

pdf(save_pdf("tsne_s_all_subset"),width = 7.5)
DimPlot(s.all.subset, label = F)+
  NoLegend()
dev.off()

```


# Number of cells in each cluster (10x and Celseq2)

```{r}

s.all.subset$seurat_clusters <- factor( s.all.subset$seurat_clusters, levels = mixedsort(unique(s.all.subset$seurat_clusters)))

df <- table(s.all.subset$seurat_clusters,s.all.subset$time) %>% 
  as.data.frame() %>% 
  set_colnames(c("Idents","time","number_cells")) %>% 
  mutate(time = toupper(time))

df$Idents <- factor(df$Idents, levels = mixedsort(unique(as.character(df$Idents))))

df.tmp <- df %>% group_by(Idents) %>% 
  summarise(number_total = sum( number_cells)) %>% 
  arrange(desc(number_total)) %>% 
  mutate(id = 1:43)

number_of_bar <- 43
angle <-  90 - 360 * (df.tmp$id-0.5) /number_of_bar  

df.tmp$hjust <- ifelse( angle < -90, 1, 0)

df.tmp$angle <-ifelse(angle < -90, angle+180, angle)


pdf(save_pdf("number_of_cells_in_each_cluster"), width = 12)

p <- ggplot(df, aes(x=Idents, y=number_cells, fill = time)) + 
  geom_bar(stat="identity") +
  scale_fill_brewer(palette = "Set2")+
  # scale_fill_viridis_d() +
  ylim(-100,700) +
  theme_minimal() +
  theme(
    legend.title = element_blank(),
    axis.text = element_blank(),
    axis.title = element_blank(),
    panel.grid = element_blank(),
    plot.margin = unit(rep(-1,4), "cm")) +
  coord_polar(start = 0) +
  geom_text(data=df.tmp, aes(x=id, y=number_total+10, label=Idents, hjust=hjust), 
            color="black", 
            fontface="bold",
            alpha=0.8, 
            size=2.5, 
            angle= df.tmp$angle, 
            inherit.aes = FALSE )

print( p ); dev.off();
```



# plot tsne and feature plots, after remove opque cells

```{r}

pdf(save_pdf("tsne_plot_group_by_method_"),width = 8)
DimPlot( s.all.subset,group.by = "method")+
  theme_void()+
  scale_color_manual(values = c("#CD5555", "#1E90FF"))
dev.off()

pdf(save_pdf( "feature_plot_Dh31_" ) ,width = 8)
f.feature.tsne(Gene = "Dh31",s.in = s.all.subset)+
    theme_void()
dev.off()

pdf(save_pdf( "feature_plot_AstC_" ) ,width = 8)
f.feature.tsne(Gene = "AstC",s.in = s.all.subset)+
  theme_void()
dev.off()

pdf(save_pdf( "feature_plot_Dh44_" ) ,width = 8)
f.feature.tsne(Gene = "Dh44",s.in = s.all.subset)+
  theme_void()
dev.off()

pdf(save_pdf( "feature_plot_Ms_" ) ,width = 8)
f.feature.tsne(Gene = "Ms",s.in = s.all.subset)+
  theme_void()
dev.off()


```


# ple, dat, tim amd clk expression in boxplot 

```{r}

df <- expm1(s.all.subset@assays$RNA@data);

Gene <- c("tim","Clk","DAT","ple","Pdp1","Vmat","Nos","Fer2", "Dh44")

  
df.loc <- as.data.frame(df[Gene,]) %>% 
  t() %>% as.data.frame() %>% 
  rownames_to_column()
  
Idents(s.all.subset) <- s.all.subset@active.ident
  
df.loc$cluster <- Idents(s.all.subset)[df.loc$rowname]

l.clk.clusters <- c(0,1,2,3,5,6,7,10,11,12,14,15,16,18,25,29,32,34,38)
l.th.clusters <- c(4,8,9,13,17,19,20,21,22,23,24,26,27,28,30,31,33,35,36,37,39,41,42,43)


p1 <- ggplot(df.loc,aes(x=cluster,y=tim)) + 
  geom_jitter(alpha=0.5, color = c("#CD5555")) + 
  theme_cowplot() +
  geom_boxplot(notch = FALSE,width = 0.4,color="gray50",alpha = 0.5, outlier.color = c("#FFFFFF"),outlier.alpha = 0.001)+
  theme(axis.text.x = element_text(angle = 90,hjust = 1,vjust = 0.5),legend.position = "top",
          legend.title = element_blank()) +
  scale_y_continuous(breaks = round(seq(min(df.loc$tim), max(df.loc$tim)*0.8, by = max(df.loc$tim)/5 ))) +
  ylim(min(df.loc$tim), max(df.loc$tim)*0.8)+
  labs(x="",y="tim")


p2 <- ggplot(df.loc,aes(x=cluster,y=Clk)) + 
  geom_jitter(alpha=0.5, color = c("#1874CD")) + 
  theme_cowplot() +
  geom_boxplot(notch = FALSE,width = 0.4,color="gray50",alpha = 0.5, outlier.color = c("#FFFFFF"),outlier.alpha = 0.001)+
  theme(axis.text.x = element_text(angle = 90,hjust = 1,vjust = 0.5),legend.position = "top",
          legend.title = element_blank()) +
  scale_y_continuous(breaks = round(seq(min(df.loc$Clk), max(df.loc$Clk)*0.8, by = max(df.loc$Clk)/5 ))) +
  ylim(min(df.loc$Clk), max(df.loc$Clk)*0.8)+
  labs( x="",y="Clk")


 #c("#548B54", "#CDBA96")
 
p3 <- ggplot(df.loc,aes(x=cluster,y=ple)) + 
  geom_jitter(alpha=0.5, color = "#548B54") + 
  theme_cowplot() +
  geom_boxplot(notch = FALSE,width = 0.4,color="gray50",alpha = 0.5, outlier.color = c("#FFFFFF"),outlier.alpha = 0.001)+
  theme(axis.text.x = element_text(angle = 90,hjust = 1,vjust = 0.5),legend.position = "top",
          legend.title = element_blank()) +
  scale_y_continuous(breaks = round(seq(min(df.loc$ple), max(df.loc$ple)*0.8, by = max(df.loc$ple)/5 ))) +
  ylim(min(df.loc$ple), max(df.loc$ple)*0.8)+
  labs( x="",y="ple")


p4 <- ggplot(df.loc,aes(x=cluster,y=DAT)) + 
  geom_jitter(alpha=0.5, color = c("#CDBA96")) + 
  theme_cowplot() +
  geom_boxplot(notch = FALSE,width = 0.4,color="gray50",alpha = 0.5, outlier.color = c("#FFFFFF"),outlier.alpha = 0.001)+
  theme(axis.text.x = element_text(angle = 90,hjust = 1,vjust = 0.5),legend.position = "top",
          legend.title = element_blank()) +
  scale_y_continuous(breaks = round(seq(min(df.loc$DAT), max(df.loc$DAT)*0.8, by = max(df.loc$DAT)/5 ))) +
  ylim(min(df.loc$DAT), max(df.loc$DAT)*0.8)+
  labs( x="",y="DAT")


p5 <- ggplot(df.loc,aes(x=cluster,y=Vmat)) + 
  geom_jitter(alpha=0.5, color = c("#2F4F4F")) + 
  theme_cowplot() +
  geom_boxplot(notch = FALSE,width = 0.4,color="gray50",alpha = 0.5, outlier.color = c("#FFFFFF"),outlier.alpha = 0.001)+
  theme(axis.text.x = element_text(angle = 90,hjust = 1,vjust = 0.5),legend.position = "top",
          legend.title = element_blank()) +
  scale_y_continuous(breaks = round(seq(min(df.loc$Vmat), max(df.loc$Vmat)*0.8, by = max(df.loc$Vmat)/5 ))) +
  ylim(min(df.loc$Vmat), max(df.loc$Vmat)*0.8)+
  labs( x="",y="Vmat")

p6 <- ggplot(df.loc,aes(x=cluster,y=Pdp1)) + 
  geom_jitter(alpha=0.5, color = c(c("#9FB6CD"))) + 
  theme_cowplot() +
  geom_boxplot(notch = FALSE,width = 0.4,color="gray50",alpha = 0.5, outlier.color = c("#FFFFFF"),outlier.alpha = 0.001)+
  theme(axis.text.x = element_text(angle = 90,hjust = 1,vjust = 0.5),legend.position = "top",
          legend.title = element_blank()) +
  scale_y_continuous(breaks = round(seq(min(df.loc$Pdp1), max(df.loc$Pdp1)*0.8, by = max(df.loc$Pdp1)/5 ))) +
  ylim(min(df.loc$Pdp1), max(df.loc$Pdp1)*0.8)+
  labs( x="",y="Pdp1")



p7 <- ggplot(df.loc,aes(x=cluster,y=Nos)) + 
  geom_jitter(alpha=0.5, color = c("#2F4F4F")) + 
  theme_cowplot() +
  geom_boxplot(notch = FALSE,width = 0.4,color="gray50",alpha = 0.5, outlier.color = c("#FFFFFF"),outlier.alpha = 0.001)+
  theme(axis.text.x = element_text(angle = 90,hjust = 1,vjust = 0.5),legend.position = "top",
          legend.title = element_blank()) +
  scale_y_continuous(breaks = round(seq(min(df.loc$Nos), max(df.loc$Nos)*0.8, by = max(df.loc$Nos)/5 ))) +
  ylim(min(df.loc$Nos), 40)+
  labs( x="",y="Nos")

p8 <- ggplot(df.loc,aes(x=cluster,y=Fer2)) + 
  geom_jitter(alpha=0.5, color = c(c("#1874CD"))) + 
  theme_cowplot() +
  geom_boxplot(notch = FALSE,width = 0.4,color="gray50",alpha = 0.5, outlier.color = c("#FFFFFF"),outlier.alpha = 0.001)+
  theme(axis.text.x = element_text(angle = 90,hjust = 1,vjust = 0.5),legend.position = "top",
          legend.title = element_blank()) +
  scale_y_continuous(breaks = round(seq(min(df.loc$Fer2), max(df.loc$Fer2)*0.8, by = max(df.loc$Fer2)/5 ))) +
  ylim(min(df.loc$Fer2), 15)+
  labs( x="",y="Fer2")


p9 <- ggplot(df.loc,aes(x=cluster,y=Dh44)) + 
  geom_jitter(alpha=0.5, color = "#548B54") + 
  theme_cowplot() +
  geom_boxplot(notch = FALSE,width = 0.4,color="gray50",alpha = 0.5, outlier.color = c("#FFFFFF"),outlier.alpha = 0.001)+
  theme(axis.text.x = element_text(angle = 90,hjust = 1,vjust = 0.5),legend.position = "top",
          legend.title = element_blank()) +
  scale_y_continuous(breaks = round(seq(min(df.loc$Dh44), max(df.loc$Dh44)*0.8, by = max(df.loc$Dh44)/5 ))) +
  ylim(min(df.loc$Dh44), max(df.loc$Dh44)*0.8)+
  labs( x="",y="Dh44")








pdf(save_pdf("tim_expression_in_all_clusters"),width = 10, height = 2.5)
p1
dev.off()

pdf(save_pdf("Clk_expression_in_all_clusters"),width = 10, height = 2.5)
p2
dev.off()

pdf(save_pdf("ple_expression_in_all_clusters"),width = 10, height = 2.5)
p3
dev.off()

pdf(save_pdf("DAT_expression_in_all_clusters"),width = 10, height = 2.5)
p4
dev.off()

pdf(save_pdf("Vmat_expression_in_all_clusters"),width = 10, height = 2.5)
p5
dev.off()

pdf(save_pdf("Pdp1_expression_in_all_clusters"),width = 10, height = 2.5)
p6
dev.off()

pdf(save_pdf("Nos_expression_in_all_clusters"),width = 10, height = 2.5)
p7
dev.off()

pdf(save_pdf("Fer2_expression_in_all_clusters"),width = 10, height = 2.5)
p8
dev.off()









f.feature.tsne(Gene = "Proc",s.in = s.all.subset)




library( qgraph )

?qgrah
  
```



# sanky diagram, supplemental figure 3

```{r}
s.clk <- readRDS("~/Desktop/clk856_figures/raw_rds/dm_clock_neurons_39_raw_clustering.rds")

s.clk <- subset(s.clk, cells = s.clk$cell.names[s.clk$experiment == "CLK856_LD"])

df.1 <- s.all.subset@meta.data %>% 
  filter(seurat_clusters %in% l.clk.clusters,
         method == "Celseq2") %>% 
  select(cell.names, renamed_idents)

df.2 <- s.clk@meta.data %>% 
  select(cell.names, Idents)


links <- left_join(df.1, df.2, by = "cell.names") %>% 
  mutate( Idents = as.character(Idents)) %>% 
  replace_na(list(Idents ="TH-GAL4")) %>% 
  count(renamed_idents,Idents) %>% 
  select( Idents, everything()) %>% 
  set_colnames(c("source", "target", "value"))

# From these flows we need to create a node data frame: it lists every entities involved in the flow
nodes <- data.frame(
  name=c(mixedsort(as.character(links$source)), 
         mixedsort(as.character(links$target))) %>% unique()
)

# With networkD3, connection must be provided using id, not using real name like in the links dataframe.. So we need to reformat it.
links$IDsource <- match(links$source, nodes$name)-1 
links$IDtarget <- match(links$target, nodes$name)-1


# Make the Network
library( networkD3 )
p <- sankeyNetwork(Links = links, Nodes = nodes,
                   Source = "IDsource", Target = "IDtarget",
                   Value = "value", NodeID = "name", 
                   units = 'TWh', 
                   fontSize = 18, 
                   nodeWidth = 30,
                   fontFamily="Times New Roman", 
                   iterations = 1,
                   sinksRight=TRUE)

# set iteration = 0, the nodes will appear just as in the links dataframe.

library(htmlwidgets)
saveWidget(p, file="Figure_plot_2/cell_infor_sankeyColor3_0308.html")


library(webshot)
#install phantom:
# webshot::install_phantomjs()

# Make a webshot in pdf : high quality but can not choose printed zone
webshot("file:///Users/dingbangma/Documents/GitHub/10X_Clk856_TH/Figure_plot_2/cell_infor_sankeyColor3_0308.html", "Figure_plot_2/sanky_plot_clock_cell_info_0308.pdf", delay = 0.2)


```

# heatmap GPCR and TFs

```{r}

# based on ple and time expression

l.clk.clusters <- c(0,1,2,3,5,6,7,10,11,12,14,15,16,18,25,29,32,34,38)
l.th.clusters <- c(4,8,9,13,17,19,20,21,22,23,24,26,27,28,30,31,33,35,36,37,39,41,42,43)

s.clk.sub <- subset(s.all.subset, cells = s.all.subset$cell.names[s.all.subset$seurat_clusters %in% l.clk.clusters])
# df.m.clk <- FindAllMarkers( s.clk.sub, test.use="negbinom", only.pos=FALSE, assay="RNA", verbose=TRUE  )
# write.csv(df.m.clk, file = paste0("data/marker_genes_just_in_clock_neurons_", Sys.Date(),".csv"))

s.th.sub <- subset(s.all.subset, cells = s.all.subset$cell.names[s.all.subset$seurat_clusters %in% l.th.clusters])

# df.m.th <- FindAllMarkers( s.th.sub, test.use="negbinom", only.pos=FALSE, assay="RNA", verbose=TRUE  )
# write.csv(df.m.th, file = paste0("data/marker_genes_just_in_TH_neurons_", Sys.Date(),".csv"))


df.m.clk <- read.csv("data/marker_genes_just_in_clock_neurons_2021-11-24.csv", row.names = 1)
df.m.th <- read.csv("data/marker_genes_just_in_TH_neurons_2021-11-24.csv", row.names = 1)




library(circlize)
col_fun = colorRamp2(c(-2, 0, 2), c("navy", "white", "red"))

# TFs ----------------------------

pdf(save_pdf( "TFs_expression_in_clk_neurons" ), width = 5)
f.plot.marker.heatmap(s.in = s.clk.sub,df.marker = df.m.clk,features = l.tfs)
dev.off()

pdf(save_pdf( "TFs_expression_in_TH_neurons" ), width = 6) 
f.plot.marker.heatmap(s.in = s.th.sub,df.marker = df.m.th, features = l.tfs)
dev.off()


# GPCRs -----------------------------

l.gpcr.ms <- scan("~/Documents/scRNA_seq/resource/list_GPCRs_matthias.csv", what=as.character())

pdf( save_pdf( "GPCRs_expression_in_clk_neurons" ),width = 5)
f.plot.marker.heatmap(s.in = s.clk.sub,df.marker = df.m.clk,features = l.gpcr.ms)
dev.off()

pdf(save_pdf( "GPCRs_expression_in_th_neurons" ), width = 6)
f.plot.marker.heatmap(s.in = s.th.sub,df.marker = df.m.th,features = l.gpcr.ms)
dev.off()



# CAMs -----------------------------

pdf(save_pdf( "Heatmap_cams_expression_in_clk_neurons" ),height = 9,width = 5)
f.plot.marker.heatmap(s.in = s.clk.sub,df.marker = df.m.clk,features = l.cams)
dev.off()

pdf(save_pdf( "Heatmap_cams_expression_in_th_neurons" ),height = 9,width = 6)
f.plot.marker.heatmap(s.in = s.th.sub,df.marker = df.m.th,features = l.cams)
dev.off()

```


# tim cycling in all clock neuron clusters

```{r}

DefaultAssay(s.all.subset) <- "RNA"

pdf(save_pdf("tim_cycling_in_all_clock_clusters_2"), width = 10,height = 6)
FetchData(object = s.all.subset, vars = c("tim", "classification", "seurat_clusters", "time","method")) %>%
  filter( classification == "Clock neurons") %>% 
  mutate(renamed_idents = factor(seurat_clusters, levels = mixedsort(unique(as.character( seurat_clusters ))))) %>% 
  mutate( tim = expm1( tim )) %>% 
  ggplot(aes( time, tim))+
  geom_jitter(alpha = 0.8, size=2, color = c("#9BCD9B"))+
  scale_color_brewer(palette = "Dark2")+
  facet_wrap(~seurat_clusters,ncol = 5)+
  ylim(0,80)+
  stat_summary(fun=mean, geom="point", shape=20, color= c("#CD8C95"), size=5)+
  # stat_summary(fun.data=mean_se, geom="errorbar", color= c("#CD8C95"))+
  theme(strip.background = element_blank(),
        axis.text.x = element_text(angle = 45, vjust = 0.5,hjust = 1),
        axis.line.x = element_blank(),
        axis.ticks.x = element_blank())+
  labs(x="")

dev.off()




```


# dotplot DIP dpr
```{r}

df.m <- read.csv("~/Desktop/phoebe/10x_clk856_TH/analysis/rds_data_clustering/DGE_negbinom_2021-11-24.csv",row.names = 1,stringsAsFactors = FALSE) %>% 
  filter( p_val_adj < 0.05 & avg_logFC >log(1.25))

df <- read.csv("resource/ensemblToSymbol.csv") %>% 
  pull(symbol)

l.DIP_dpr <- grep("dpr|DIP-", df, value = T, ignore.case = F)

l.dpr <- grep("dpr", l.DIP_dpr, value = T, ignore.case = F)

l.dpr <-l.dpr[l.dpr %in% df.m$gene]

l.dpr <- factor(l.dpr, levels = mixedsort( l.dpr ))


p <- DotPlot(object = s.all.subset,features = l.dpr,assay = "RNA",cols = "RdGy",dot.min = 0.0)

pdf( save_pdf("dpr expression in all clusters dotplot"), width = 15,height = 5)
f.dotplot.custom( p )
dev.off()


```


# tsne plot TH cluster in gray

```{r}

l.clk.clusters <- c(0,1,2,3,5,6,7,10,11,12,14,15,16,18,25,29,32,34,38)
l.th.clusters <- c(4,8,9,13,17,19,20,21,22,23,24,26,27,28,30,31,33,35,36,37,39,41,42,43)
l.clk.clusters.pre <- c(0,1,3,5,6,7,10,11,12,14,15,16,18,25,29,32,34,38)


p <- DimPlot(s.all.subset,reduction = "tsne") + NoLegend();
pbuild <- ggplot2::ggplot_build(p);
pdata <- pbuild$data[[1]];

pdata <-  pdata[order(pdata$group), ];
ucols <- unique(pdata$colour) ;

names(ucols) <- mixedsort(unique(as.character( Idents(s.all.subset))) );

ucols[which( names(ucols) %in% l.th.clusters)] <- c("#B5B5B5")

ucols[which( names(ucols) %in% l.clk.clusters.pre)] <- c("#F8766D")

ucols[which( names(ucols) %in% c(2))] <- c("#00BD65")



s.all.subset$renamed_idents <- as.character(s.all.subset$renamed_idents )
s.all.subset$renamed_idents[s.all.subset$renamed_idents == "2"] = "2:Clk"
s.all.subset$renamed_idents[s.all.subset$renamed_idents == 25] <- "25:DN1p(4)"

s.all.subset$renamed_idents %>% as.character() %>% unique()


df <- as.data.frame( s.all.subset@reductions$tsne@cell.embeddings );
  
df$ident <- (Idents(s.all.subset)[])
df$renamed_idents <- s.all.subset$renamed_idents
  
 
df_mini <- df[!duplicated(df$ident),]


pdf(save_pdf("tsne_clk_color_th_gray"),width = 8)
DimPlot(s.all.subset,cols = ucols, label = F)+
  NoLegend()+
  geom_text_repel(data =df_mini[!(df_mini$renamed_idents %in% l.th.clusters), ],
                  aes( x=tSNE_1, y=tSNE_2, label= renamed_idents),
                  family = "Arial",
                  size = 5,
                  nudge_x = .15,
                  box.padding = 0.5,
                  nudge_y = 1,
                  segment.curvature = -0.1,
                  segment.ncp = 3,
                  segment.angle = 20,
    )
dev.off()



```


# VGlut in two colors

```{r}

l.genes <- "VGlut"

DefaultAssay( s.all.subset ) <- "RNA"
  
df <- as.data.frame( s.all.subset@reductions$tsne@cell.embeddings );
  
df$ident=(Idents(s.all.subset)[])
  
df.tp10k <- FetchData(s.all.subset,vars = c( l.genes,"renamed_idents", "seurat_clusters"),slot = "data") %>% 
   mutate( VGlut = expm1( VGlut ))

df <- cbind( df, df.tp10k[rownames( df ),])

  
df_mini <- df[!duplicated(df$ident),]


l.cluster.plot <- df %>% group_by(ident) %>% 
  summarise(mean = mean(VGlut)) %>% 
  arrange( desc( mean )) %>% 
  top_n(n = 13,wt = mean) %>% 
  pull(ident) %>% 
  as.character()

df_mini_2 <- df_mini %>% 
  filter( ident %in% l.cluster.plot)


pdf( save_pdf("VGlut_expression_in_TH_neurons_clock_neurons"), width = 9)
ggplot(mapping = aes(tSNE_1, tSNE_2)) +
  geom_point( data=df, colour="grey75", size=1.0, alpha=0.5, shape=16 )+
  geom_point( data=df[ df$seurat_clusters %in% l.clk.clusters, ], aes(color= VGlut) , size=1.0, alpha=0.5, shape=16 ) + 
  scale_color_gradientn( colors=c("grey75", "red","red1", "red2", "red3", "red4", "black" ), name = "VGlut in Clk")+
  new_scale_color()+
  geom_point( data=df[df$seurat_clusters %in% l.th.clusters, ], aes(color= VGlut), size=1.0, alpha=0.5, shape=16 ) + 
  scale_color_gradientn( colors=c("grey75", "purple", "purple1", "purple2", "purple3", "purple4","Black"), name ="VGlut in TH")+ 
  theme_cowplot()+
  geom_text_repel(data =df_mini_2,aes( x=tSNE_1, y=tSNE_2, label= renamed_idents),
                  size = 5,
                  family = "Arial",
                  nudge_x = .15,
                  box.padding = 0.5,
                  nudge_y = 1,
                  segment.curvature = -0.1,
                  segment.ncp = 3,
                  segment.angle = 20)
dev.off()

```


# tsne plot gene expression

```{r}

pdf(save_pdf("triple_color_Pdf_Trissin_CCHa1"))
f.feature.tsne.v2(Gene = c("Pdf","Trissin","CCHa1"),s.in = s.all.subset,threshold = 5)
dev.off()

pdf(save_pdf("triple_color_Pdf_Trissin_CCHa1"),width = 8.5)
f.feature.tsne.v2(Gene = c("Pdf","Trissin","CCHa1"),s.in = s.all.subset,threshold = 5)+
  scale_y_continuous(sec.axis = dup_axis()) +
  scale_x_continuous(sec.axis = dup_axis())
dev.off()


```


# Heatmap of neuropeptides expression in clock neurons and TH neurons

```{r}
v.features.npp <- scan("~/Documents/scRNA_seq/resource/neuropeptides_55.txt",what = character())

v.features.npp <- v.features.npp[v.features.npp %in% rownames(s.all.subset@assays$RNA@counts)]


df.marker <- df.m %>% filter(p_val_adj <0.05, avg_logFC > log(1.25), TP10K.mean > 2);


v.genes.plot <- intersect(unique(df.marker$gene),v.features.npp)

s.all.subset$seurat_clusters <- factor(s.all.subset$seurat_clusters, levels = c(l.clk.clusters, l.th.clusters))

  
df <- sapply(split(s.all.subset$cell.names,s.all.subset$seurat_clusters),function(cells){
    apply(s.all.subset@assays$RNA@scale.data[v.genes.plot,cells],1,mean)
  })
    

library(circlize)
col_fun = colorRamp2(c(-2, 0, 2), c("navy", "white", "red"))

pdf(save_pdf("heatmap_neuropeptides_clock_TH"), height = 5);

ComplexHeatmap::Heatmap(df,
                        cluster_columns = FALSE,
                        cluster_rows = FALSE,
                        name = "scaled",
                        row_dend_width = unit(2, "cm"),
                        column_title = "",
                        col = col_fun,
                        border = TRUE,
                        top_annotation = HeatmapAnnotation(foo = anno_block(gp = gpar(fill = 3:4), 
                                                                            labels = c("Clock neurons","TH neurons"),
                                                                            labels_gp = gpar(col = "white", fontsize = 10))),
                        column_split = c(rep("Clock neurons", 19),rep("TH neurons", 24)));
dev.off();

```


# gene category in highly variables

```{r}

l.genes <- list(l.tfs, l.gpcr.ms, l.cams, l.npp, l.RBP, l.cstrans, l.ics)

names(l.genes ) <- c("TF","GPCR","CAM","Neuropeptides","RBP","CST","ICS")

df <- data.frame("total" = rep(NA, 7), "in_variable" = rep(NA,7))

DefaultAssay(s.all.subset) <- "integrated"
l.variables <- VariableFeatures( s.all.subset )


for( i in seq_along(l.genes)){
  df[i,] <- list(length(l.genes[[i]]), sum(l.genes[[i]] %in% l.variables))
}

df$gene_group <- names(l.genes)

pdf(save_pdf("gene_cat_highly_variables"), width = 7.5, height = 4)
df %>% 
  ggplot(aes(fct_reorder( gene_group, in_variable), in_variable, fill = gene_group))+
  geom_col()+
  coord_flip()+
  geom_text(aes(label = in_variable), vjust = -0.5)+
  scale_fill_viridis_d()+
  theme(legend.position = "none",
        axis.text.x = element_text(angle = 45, hjust = 1, vjust = -0.5))+
  labs(x="", y="Number of genes")
dev.off()



```


# network, gene expression correlation

```{r}

l.clusters <- as.character( s.all.subset$renamed_idents ) %>% unique()

l.clk.clusters <- c( grep(":", l.clusters, value = T))
l.th.clusters <- setdiff( l.clusters, l.clk.clusters)

```

```{r}

l.clusters <- s.all.subset$renamed_idents %>% as.character() %>% unique()

s.all.subset$renamed_idents <- factor(s.all.subset$renamed_idents, levels = c(grep(":",l.clusters, value = TRUE), l.clusters[!grepl(":",l.clusters)]))


l.test <- l.tfs

f.gene.correlation.net <- function( gene_list, threshod = 0.4 ){
  
  l.test <- gene_list
  
  l.test <- l.test[l.test %in% rownames( s.all.subset )]
  
  m.mtrx <- sapply( split( s.all.subset$cell.names, s.all.subset$renamed_idents ), FUN = function(cells){
    apply(s.all.subset@assays$RNA@scale.data[l.test, cells], 1, mean)
  })
  
  
  cor.mtest <- function(mat, ...) {
    mat <- as.matrix(mat)
    n <- ncol(mat)
    p.mat<- matrix(NA, n, n)
    diag(p.mat) <- 0
    for (i in 1:(n - 1)) {
      for (j in (i + 1):n) {
        tmp <- cor.test(mat[, i], mat[, j], method = "spearman", ...)
        p.mat[i, j] <- p.mat[j, i] <- tmp$p.value
      }
    }
    colnames(p.mat) <- rownames(p.mat) <- colnames(mat)
    p.mat
  }
  
  
  p.mat <- cor.mtest(m.mtrx)
  
    test <- cor(m.mtrx, method = "spearman")
  
  # corrplot(test, p.mat = p.mat, sig.level = 0.05, insig = "blank", type = "full", tl.col = "black")
  
  
  
  test_net <- test
  
  for (i in 1:nrow(test_net)){
    for (j in 1:ncol(test_net)){
      if(p.mat[i,j] > 0.05){
        test_net[i,j] <- 0
      }
      if(test_net[i,j] == 1){
        test_net[i,j] <- 0
      }
    }
  }
  
  
  l.group <- list()
  
  l.group$"Clock Neurons" <- which( colnames(m.mtrx) %in% l.clk.clusters)
  l.group$"TH Neurons" <- which( colnames(m.mtrx) %in% l.th.clusters)
  
  p <- qgraph(test_net, 
       layout = "spring", 
       # directed = TRUE, 
       threshold = threshod,
       groups = l.group,
       labels=colnames(test_net),
       label.color = "black",
       label.scale = F, 
       label.cex = 0.9,
       theme = "colorblind", 
       vsize = 5.5, 
       edge.labels = FALSE, 
       esize = 8, 
       # label.prop=0.99,
       color = c( "#58B5BC", "#CDCDC1"),
       border.color = "white",
       border.width = 2,
       edge.color = "steelblue", 
       edge.width = 0.8,
       curve = 0.01,
       curveAll = FALSE,
       legend = FALSE
       )
  
  return( p )
  
  
}
```

```{r}

pdf(save_pdf("TF_gene_expression_correlation_newtork"),width = 10, height = 10)
print( f.gene.correlation.net(gene_list = l.tfs,threshod = 0.4))
dev.off()


pdf(save_pdf("GPCRs_gene_expression_correlation_newtork"),width = 10, height = 10)
print( f.gene.correlation.net(gene_list = l.gpcr.ms))
dev.off()


pdf(save_pdf("npp_gene_expression_correlation_newtork"),width = 10, height = 10)
print( f.gene.correlation.net(gene_list = l.npp,threshod = 0.55))
dev.off()


pdf(save_pdf("CAM_gene_expression_correlation_newtork"),width = 10, height = 10)
print( f.gene.correlation.net(gene_list = l.cams,threshod = 0.4))
dev.off()



```


# Build cluster tree
```{r}

library(ggtree)

DefaultAssay( s.all.subset )

s.all.subset$renamed_idents <- as.character(s.all.subset$renamed_idents )
s.all.subset$renamed_idents[s.all.subset$renamed_idents == "2"] = "2:Clk"
s.all.subset$renamed_idents[s.all.subset$renamed_idents == 25] <- "25:DN1p(4)"

Idents( s.all.subset ) <- s.all.subset$renamed_idents

s.all.subset <- BuildClusterTree(s.all.subset)

PlotClusterTree(s.all.subset)

myPhyTree <- Tool(object=s.all.subset, slot = "BuildClusterTree")


pdf( save_pdf("Hierachical_cluster_circle"), width = 10, height = 10)

# layout - daylight 

ggtree(myPhyTree,layout="circular")+
  geom_tiplab(family="Arial")+
  geom_hilight(node = 48, fill = "steelblue", alpha = 0.6,extend = 0)+
  geom_hilight(node = 49, fill = "darkgreen", alpha = 0.6, extend = 0)
  theme_tree()+
  xlim(NA,1200)

dev.off()

```

